The COVID-19 Pandemic's Impact on Bullying Search Intensity with respect to Asian Population

### 2023-02-22 Outputs/Paper/paper.qmd

---
title: "The COVID-19 Pandemic's Impact on Bullying Search Intensity with respect to Asian Population"
author: 
  - Will Davidson
  - Jason Ngo
  - Annie Yan
thanks: "Code and data are available at: https://github.com/AnnieYan0807/Analysis-on-The-COVID-19-Pandemic-Disrupted-Both-School-Bullying-and-Cyberbullying. The replication on the SSRP can be found at : https://doi.org/10.48152/ssrp-54f4-p919"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "The Covid-19 pandemic incited a wave of anti-Asian hate crimes across the United States. This paper analyzes how school closures and the shift to online learning impacted searches about bullying in states with high and low Asian population with a comparison to pre-pandemic dates and with in-person learning. Results suggest that while the overall trend in bullying of high school students has been in decline nationwide between 2016-2021, with a larger drop during Covid-19, the states with high percentages of Asian populations saw a higher intensity of bullying searches when compared to states with low percentages of Asian populations over the six year period. These findings tell two stores: One of declining bullying trends in the US school system and one showing that anti-Asian bullying is not a result of Covid-19, but rather a sympton of a pre-existing systemic racism in our learning institutions."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Anti-Asian violence skyrocketed over the pandemic. The Center for the Study of Hate and Extremism published a report showing how anti-Asian hate crimes grew by 339% last year compared to the year before. These hate crimes were fueled by the pandemic, mainly occurring in highly populated urban cities like New York, San Francisco, and Los Angeles. The percentages of Asian hate crimes in New York rose from 30 to 133 and in San Francisco from 9 to 60. American culture pretends Asian-Americans face no discrimination or racism. There were countless examples where when the U.S. was faced with an economic downturn, Asian Americans were affected. The 1982 killing of Vincent Chin in Detroit came after the 1980-1982 Detroit recession and The Page Act of 1875, America's first immigration law that banned Chinese women after the Great Panic of 1873. It's safe to assume an economic horror like the pandemic would lead to hate. It was disconcerting reading about the different hate acts that occurred, and it was clear there needed to be culturally appropriate and accessible community safety programs. From the data provided, we decided to clean it, focusing on the states with an Asian population. There has been mainstream media coverage of anti-Asian racism but little effort toward the Asian American Youth.

>>>>

---
title: "The COVID-19 Pandemic's Impact on Bullying Search Intensity with respect to Asian Population"
author: 
  - Will Davidson
  - Jason Ngo
  - Annie Yan
thanks: "Code and data are available at: https://github.com/AnnieYan0807/Analysis-on-The-COVID-19-Pandemic-Disrupted-Both-School-Bullying-and-Cyberbullying. The replication on the SSRP can be found at : https://doi.org/10.48152/ssrp-54f4-p919"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "The Covid-19 pandemic incited a wave of anti-Asian hate crimes across the United States including derogatory language in the media, random bullying, and violent, senseless murders. This paper analyzes how high school closures and the shift to online learning by schools throughout the pandemic, impacted incidents of bullying of Asian students compared to non Asian students when compared to pre-pandemic trends and in-person learning. Results suggest that while the overall trend in bullying of high school students has been in decline across all states between 2016-2021, with a larger drop during Covid-19, the states with high Asian populations saw greater incidents of bullying when compared to states with low Asian populations over the six year period. These findings tell both a good news story of declining bullying trends in the US school system and a highly concerning narrative that anti-Asian bullying is not a result of Covid-19, but rather an intensified awareness of pre-existing racism.
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Anti-Asian violence skyrocketed during the Covid-19 pandemic. The Center for the Study of Hate and Extremism published a report showing how anti-Asian hate crimes in the United States grew by 339% from 2020 to 2021 - the height of the global crisis. This increase in racism, fueled by the pandemic, occurred mainly in highly populated urban cities where the population of people of Asian descent are more predominant. For example, the percentages of Asian hate crimes in New York rose from 30% to 133% and in San Francisco from 9% to 60%. American culture pretends Asian Americans face no discrimination or racism. There are countless examples where when the U.S. was faced with an economic downturn, Asian Americans were affected. The 1982 killing of Vincent Chin in Detroit came after the 1980-1982 Detroit recession and The Page Act of 1875, America's first immigration law that banned Chinese women after the Great Panic of 1873. It's safe to assume an economic horror like the pandemic would lead to hate. It was disconcerting reading about the different hate acts that occurred, and it was clear there needed to be culturally appropriate and accessible community safety programs. From the data provided, we decided to clean it, focusing on the states with an Asian population. There has been mainstream media coverage of anti-Asian racism but little effort toward the Asian American Youth.
